Sushi monster

### 2025-02-16 inst/sushi.Rmd
how long to run without cache
better range

@@

```{r calclikesushi, cache=TRUE}
f <- function(strength){
   H <- make_sushi_H(a[wanted,-1], strength=strength)
   maxp(H,give=1)$`Log-likelihood`
}
s <- seq(from=1.4,to=7.5,len=5)
L <- sapply(s,f)
```

@@

>>>>

<font size="1"> most of the time is taken calculating the
`calclikesushi` chunk.  With a sample size of 500 in chunk `tryH`, and
`n=5` in `calclikesushi`, it takes about half an hour to run without
cache. </font>

@@

```{r calclikesushi, cache=TRUE}
f <- function(strength){
   H <- make_sushi_H(a[wanted,-1], strength=strength)
   maxp(H,give=1)$`Log-likelihood`
}
s <- seq(from=1.4,to=4,len=8)
L <- sapply(s,f)
```

@@

```{r label=justtryf1, cache=TRUE}
f1 <- f(1)
```

```{r label=showf1}
f1 - max(L)
```
